%_______________________________________________
% @brief    LaTeX2e Resume for Hyeyoung Shin
\documentclass[margin,line]{resume}
\usepackage{url}
\usepackage[shortlabels]{enumitem}
%\usepackage{enumitem}

\usepackage{graphicx}

\usepackage[usenames,dvipsnames]{color}
\definecolor{light-gray}{gray}{0.70}
\definecolor{gray}{gray}{0.50}
\definecolor{dark-gray}{gray}{0.30}

\usepackage[colorlinks=true]{hyperref}

\hypersetup{
     citecolor    = gray,
     urlcolor=Blue
     %% linkcolor=Emerald
}


\usepackage{ifthen}
\usepackage[LabelsAligned]{currvita}     
\begin{document}

\newcommand{\Hawaii}{Hawai\kern.05em`\kern.05em\relax i}
\newcommand{\Manoa}{M\=anoa}

\name{{\Large Hyeyoung Shin} \hskip104mm {\large\sc Curriculum Vit\ae}}

\begin{resume}

    %___________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}
     1550 Kanalui Street            \hfill tel: 212-535-8565\\
     Honolulu, HI 96816                 \hfill url: \href{https://github.com/hyeyoungshin}{github.com/hyeyoungshin}\\
     USA  \hfill             \hfill email:  \href{mailto:hyeyoungshinw@gmail.com}{hyeyoungshinw@gmail.com}

    %__________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Interests}

    Functional programming, logic, computability, type theory.
    
    %________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{University of Hawaii at Manoa}:  %\hfill Ames, IA\\
    \textsl{Nondegree Graduate, Mathematics}\hfill 2016--present

    \textbf{\hred{http://www.cs.bham.ac.uk/~pbl/mgs2016/ }{Midlands Graduate School}}: %\hfill Birmingham, UK\\
    \textl{the Foundations of Computing Science}\hfill 11--15 April,
    2016 

    \textbf{\hred{http://www.cs.bham.ac.uk/~pbl/mgs2016/ }{Midlands Graduate School}}: %\hfill Birmingham, UK\\
    \textl{the Foundations of Computing Science}\hfill 11--15 April, 2016 

    \textbf{Iowa State University}:  %\hfill Ames, IA\\
    \textsl{Nondegree Graduate, Computer Science}\hfill 2015--2016

    \textbf{Iowa State University}:  %\hfill Ames, IA\\
    \textsl{Nondegree Undergraduate, Computer Science}\hfill 2014--2015
        
    \textbf{University of \Hawaii}: \textsl{Exchange Student Program}\hfill  2007--2008  
        
    \textbf{Kyeongpook National University}:  %\hfill Daegu, South Korea\\
    \textsl{Bachelor of English Language and Literature}\hfill 2009



      
    %_______________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}
    \textbf{Iowa State University}\\
    \textsl{Coms 228 TA:} TA for Data Structures course. \hfill Fall
    2015

    \textbf{Gyeongsan Girls' High School}\\
    \textsl{English teacher:} Teach English and advise English newspaper club.  \hfill 2009--2013


%% --- Translation Work ----
   % \textbf{Daegu District Court} \hfill 2009--2013\\
   %\textsl{Appointed translator:} \href{http://daegu.scourt.go.kr}{Daegu District Court}.

   % \textbf{Super Couple Diary} \hfill 2012\\
   % \textsl{Korean-English translator:}              
   % \href{http://supercouple.interest.me/}{Super Couple Diary}, StoryOn channel.

   %  \textbf{Daegu Embeded Conference}  \hfill 2009\\
   % \textsl{Korean-English translator:} Daegu Digital Industry Promotion Agency.

    
    %_______________________________________________________________    %         Volunteer work
    \section{\mysidestyle Volunteer\\Work}

    \textbf{InDaegu} \hfill 2011--2012\\
    \textsl{Korean-English translator:} 
    \href{http://www.in-daegu.com/}{InDaegu newspaper}.
%    \href{http://www.in-daegu.com/}{(in-daegu.com)}. 
    
        \textbf{Daegu Pockets}  \hfill 2010--2011\\
    \textsl{Korean-English translator:}
    \href{http://daegupockets.com/}{Daegu Pockets magazine}.
%    \href{http://daegupockets.com/}{(daegupockets.com).}
    
    \textbf{Daegu International Bodypainting Festival}  \hfill 2010\\
    \textsl{Korean-English translator:} DIBF Association.
    
    \textbf{Daegu International Musical Festival}   \hfill 2009\\
    \textsl{Korean-English translator:} DIMP Association.
 

%\vspace{-1cm}
%\begin{center}
%\hfill (page 1 of 4)
%\end{center}
%\newpage

    %______________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Computing Experience} 
     
    \textbf{Scala.} Course work with certificate: Functional Programming Principles in
    Scala, by Martin Odersky (Coursera)

    \textbf{Java.} Course work: Object-oriented Programming 
    ({\small COMS 227}), Data Structures ({\small COMS 228}), Algorithms ({\small COMS 311}),
    Descrete Mathematics ({\small COMS 330}), Theory of Computing ({\small COMS 331}),
    Programming Languages ({\small COMS 541}).
   
    \textbf{SML.} Course work: Programming Languages, by Dan Grossman (Coursera).

    \textbf{Other.} Eclipse, Emacs, Git, \LaTeX, Racket, Ruby.

    \section{\mysidestyle Research Experience} 
    {\bf \href{https://github.com/TypeFunc}{TypeFunc}}\\ Two semesters undergraduate reading and research in logic, functional programming, and type theory.
    
    \section{\mysidestyle Honors \& Awards} 

    {\bf \href{https://www.cs.uoregon.edu/research/summerschool/summer16/}{OPLSS
      2016}}\\
    Scolarship to atten the Oregon Programming Languages Summer School, Oregon; 20 June -2 July, 2016.
    {\bf \href{http://icfpconference.org/icfp2015/}{ICFP 2015}}\\
    Scholarship to attend the
    \href{https://www.cis.upenn.edu/~sweirich/icfp-plmw15/}{Programming 
    Languages Mentoring Workshop} at the
    20th ACM SIGPLAN International Conference on Functional Programming, 
    Vancouver, BC; 31 Aug - 2 Sep, 2015.
    {\bf \href{http://conf.researchr.org/home/PLMW-2016}{POPL/PLMW 2016}}\\
    Scolarship to atten the POPL/PLMW 2016, Florida; 19 Jan - 22 Jan, 2016.

\end{resume}
\end{document}















\section{\mysidestyle References} 

\begin{tabular}{@{}p{6cm}p{6cm}}
\textbf{Ralph Freese}       &  \textbf{William Lampe}*                  \\
Professor of Mathematics    &  Professor of Mathematics                      \\
University of Hawaii       &  University of Hawaii                      \\
2565 McCarthy Mall       &  2565 McCarthy Mall     \\
Honolulu, HI 96822     & Honolulu, HI 96822 \\
phone: 808-956-4680   &  phone: 808-956-4680 \\
email: \url{ralph@math.hawaii.edu} &  email: \url{bill@math.hawaii.edu}    \\
\end{tabular}

* Teaching references.

% EOF
